Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-15 IOPLaTeX.tex
Fixed wording

\section{Introduction}
Running molecular dynamics software has had a workflow that has not changed much over the past couple of decades.
Users of LAMMPS\cite{Plimpton1995Fast} and other codes such
as GROMACS\cite{berendsen1995gromacs}, NAMD\cite{nelson1996namd} and CHARMM\cite{brooks2009charmm} typically write
scripts in a text editor and run the scripts by passing them to the simulator on the command line.
The simulator in turn writes the results to disk and the user analyzes the results
by reading the files manually or passing them to other programs.

@@

\todo{Also mention MDDriver and GROMACS+Megamol (delalande2009complex, grottel2015megamol)}
Although this enabled real-time visualization, the workflow still involved using all these different programs which is still a problem today.

@@

Here, we present Atomify, a software that integrates script editing,
visualization and analysis into one tool.
Atomify has detailed knowledge about the inner workings of LAMMPS,
which makes it capable not only of visualizing the simulation results,
but also how the simulation is defined in terms of different groups and regions.

>>>>

\section{Introduction}
\todo[inline]{Use the word user-friendly more!}
Running molecular dynamics software has had a workflow that has not changed much over the past couple of decades.
Users of LAMMPS\cite{Plimpton1995Fast} and other codes such
as GROMACS\cite{berendsen1995gromacs}, NAMD\cite{nelson1996namd} and CHARMM\cite{brooks2009charmm} typically write
scripts in a text editor and run the scripts by passing them to the simulator on the command line.
The simulator in turn writes the results to disk and the user analyzes the results
by reading the files manually or passing them to other programs.

@@

Some 10 years later, an improved abstract communication layer called MDDriver\cite{delalande2009complex} was designed
which is general and a small effort is needed to add support for a new simulator. MegaMol\cite{grottel2015megamol} was developed
only a few years ago and supports real-time visualization of GROMACS through MDDriver.
Although this enable real-time visualizations, the workflow still involves using all these different programs and is not very user friendly.
The data is also transferred through the IMD protocol based on TCP/IP sockets\cite{delalande2009complex} which may introduce
overhead in data transfer compared to a shared memory solution.

@@

Here, we present Atomify, a software that integrates script editing,
visualization and analysis into one tool.
Atomify uses LAMMPS as a linked library and has shared memory access to the internals of LAMMPS,
which maximizes the datatransfer speed and reduces latency.
By having direct access to all the datastructures in LAMMPS, it is capable of not only of visualizing the simulation results,
but also extra information about how the simulation is defined using groups and regions.
